Results visualization across sites

### 2021-11-17 metanalysis_visualization/visualization.Rmd
added visualization for disorder group and sex ratio

>>>>

## Percentage of patients by disorder group

```{r}
perc_disorder_group_all %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date &
           disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y = percentage_dg, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  facet_grid(. ~ disorder_group) +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Percentage of patients (%)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage of patients by disorder group \n ( per ", time_period,")"))

perc_disorder_group_all %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date &
          #disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" )) %>%
          disorder_group %in% c("Suicide or Self-Injury" )) %>%
  ggplot(aes(x = time_p, y = percentage_dg, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "Percentage of patients (%)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Percentage of patients with Suicide or Self-Injury \n ( per ", time_period,")"))
```

## Sex ratio per site

```{r}
sex_ratio_by_site <- patients_hospitalized_agg_sex_perc_all %>%
  filter( sex == "female") %>%
  group_by( time_p, siteid ) %>%
  mutate( female_count = count_sex, 
          male_count = count - count_sex, 
          sex_ratio_by_site = female_count / male_count ) %>%
  select( time_p, female_count, male_count, sex_ratio_by_site, siteid)

sex_ratio_by_site %>%
    filter(time_p <= history_end_date &
         time_p >= history_start_date) %>%
  ggplot(aes(x = time_p, y = sex_ratio_by_site, fill = siteid, color = siteid)) +
  geom_point( aes(shape=siteid, color=siteid)  ) +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
   geom_hline(yintercept = 1,
             linetype = "dashed", color = "red") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  scale_x_date(date_labels = "%b-%d-%Y", breaks = "month", limits = c( history_start_date, history_end_date  )) +
  labs(y = "sex ratio (female/male)",
       x = paste0("Date (by ", time_period,")"),
       title = paste0("Sex ratio of patients with mental disorders \n ( per ", time_period,")"))
```
